---
title: "Exercise 4: DataFrrames and Tables in R"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### S Shyam Sundaram
### 19BCE1560
### 30th August, 2021
### Dr. B. Radhika Selvamani
<br>

```{r}
data<-read.csv("poker.data",header=FALSE)
head(data,10)
```
## Index
<hr/>
Click to go to the respective Question <br>
1. [Question 1](#q1) <br>
2. [Question 2](#q2) <br>
3. [Question 3](#q3) <br>
4. [Question 4](#q4)

## <a name="q1"></a> Question 1
<hr/>

Create a new data frame from the given .csv file where the 1st, 3rd, 5th , 7th and 9th columns
are factors with the levels “Heart, Spade, Diamond, Club” for values {1,2,3,4} Display the
data frame.
```{r}
colnames(data)<-c("S1","R1","S2","R2","S3","R3","S4","R4","S5","R5","Hand")
head(data,15)
co<-c("S1","S2","S3","S4","S5")
data$S1<-as.factor(data$S1)
data$S2<-as.factor(data$S2)
data$S3<-as.factor(data$S3)
data$S4<-as.factor(data$S4)
data$S5<-as.factor(data$S5)
str(data)
lev<-c("Heart","Spade","Diamond","Club")
levels(data$S1)<-lev
levels(data$S2)<-lev
levels(data$S3)<-lev
levels(data$S4)<-lev
levels(data$S5)<-lev
head(data,15)
```
## <a name="q2"></a> Question 2
<hr/>
Convert the last column into a factor where the numbers are labelled as below
0: Nothing in hand; not a recognized poker hand
1: One pair; one pair of equal ranks within five cards
2: Two pairs; two pairs of equal ranks within five cards
3: Three of a kind; three equal ranks within five cards
4: Straight; five cards, sequentially ranked with no gaps
5: Flush; five cards with the same suit
6: Full house; pair + different rank three of a kind
7: Four of a kind; four equal ranks within five cards
8: Straight flush; straight + flush
9: Royal flush; {Ace, King, Queen, Jack, Ten} + flush
Display the data frame
```{r}
data$Hand<-as.factor(data$Hand)
levels(data$Hand)<-c("Nothing in Hand","One Pair","Two Pairs","Three of a kind","Straight; five cards","Flush","Full house","Four of a kind","Straight flush","Royal flush")
head(data,15)
```
## <a name="q3"></a> Question 3
<hr/>
Display all the Three of a kind cards.
```{r}
data[data$Hand=="Three of a kind",]
```
## <a name="q4"></a> Question 4
<hr/>
Display all cards which are “Nothing in Hand” or One Pair or Two Pairs
```{r}
data[data$Hand=="Nothing in Hand" | data$Hand=="One Pair" | data$Hand=="Two Pairs",]
```

