---
title: "Lab10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### S Shyam Sundaram
### 19BCE1560
### 11th October, 2021
### Dr. B. Radhika Selvamani
<br>

## Index
<hr/>
Click to go to the respective Question <br>
1. [Question 1](#q1) <br>
2. [Question 2](#q2) <br>
3. [Question 3](#q3) <br>
4. [Question 4](#q4) <br>
5. [Question 5](#q5)

## <a name="q1"></a> Question 1
<hr/>

Q. For the Insurance data set in MASS library. Identify column types Print the summary statistics of the columns.<br><br>
A.
```{r}
library(MASS)
data(Insurance)
head(Insurance,5)
```
Types of each column
```{r}
str(Insurance)
```
We see that District, Group and Age are categorical data types. Holders and Claims are integer.<br>
Statistical summary
```{r}
summary(Insurance)
```

## <a name="q2"></a> Question 2
<hr/>

Q. Calculate the frequency , relative frequency and cumulative frequency for any categorical column and plot the bar chart and pie chart. Write your observations<br><br>
A.
Let us take the 'Districts' column, which is categorical. It is a factor with 4 levels.<br>
Frequencies:
```{r}
dist_freq = table(Insurance$District)
dist_freq
```
Relative frequencies:
```{r}
dist_rel_freq = dist_freq/nrow(Insurance)
dist_rel_freq
```
Cumulative Frequency:
```{r}
dist_cum_freq = cumsum(dist_freq)
dist_cum_freq
```
<br>Bar plot of frequencies:
```{r}
barplot(dist_freq)
```
<br>Bar plot of cumulative frequencies:
```{r}
barplot(dist_cum_freq)
```
<br>Pie chart of relative frequencies:
```{r}
pie(dist_rel_freq)
```
<br>From the plots and frequencies listed above, we see that the categories or districts for the entries are equally distributed.

## <a name="q3"></a> Question 3
<hr/>

Q. For one of the numerical columns split them into sequences. There should be at least 5 intervals. Calculate the frequency of values occurring in each interval and plot a bar plot.<br><br>
A.
We shall use the 'Holders' column.
```{r}
holders=Insurance$Holders
range(holders)
```
We have values from 3 to 3582. So, let us break it into 5 intervals with each interval having a length of 716 because (3582-3)/5 = 715.8 and we take one higher than the pper limit 3582.
```{r}
breaks=seq(3,3583, by=716)
breaks
```
Now we break the columnvalues into these intervals
```{r}
holders.cut = cut(holders,breaks,right=FALSE)
```
Frequency of each interval
```{r}
freq=table(holders.cut)
freq
```
Frequency plot of each interval
```{r}
barplot(freq)
```
<br>

## <a name="q4"></a> Question 4
<hr/>

Q. Create a scatter line plot for the cumulative frequency of the numerical column split in question 3.<br><br>
A.
```{r}
cumfreq = cumsum(freq)
cumfreq=c(0,cumfreq)
plot(breaks,cumfreq)
lines(breaks,cumfreq)
```
<br>

## <a name="q5"></a> Question 5
<hr/>

Q. Draw the scatter plot between two numerical columns and infer the correlation between them.<br><br>
A. The columns we will use are Holders and Claims.
```{r}
holders=Insurance$Holders
claims=Insurance$Claims
plot(holders,claims)
```
<br>We can see that as the Holders' axis value increases, so does Claims'. This is positively correlated.