---
title: "Lab7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### S Shyam Sundaram
### 19BCE1560
### 20th September, 2021
### Dr. B. Radhika Selvamani
<br>

## Index
<hr/>
Click to go to the respective Question <br>
1. [Question 1](#q1) <br>
2. [Question 2](#q2) <br>
3. [Question 3](#q3) <br>
4. [Question 4](#q4)

## <a name="q1"></a> Question 1
<hr/>

Q. In the realtime data available on European Exports, identify the total Export Volume in tonnes.
Find the percentage exported from India

A.
```{r}
data=read.csv("EuropeanImportsFromOtherCountries.csv",stringsAsFactors = FALSE)
head(data,1)
data$Volume=as.numeric(gsub(",","",data$Volume))
totalImports=sum(data$Volume)
totalImports
```
Total imports are thus seen above.
```{r}
ind=sum(data[data$ExportCountry=="India",]$Volume)
#ind
(ind/totalImports)*100
```

## <a name="q2"></a> Question 2
<hr/>

Q. Plot the percentage export volume of all the countries which exceed 5%. Find the global rank of India in exporting products to Europe.

A.
```{r}
library(data.table)
globtab = data.table(data$ExportCountry,data$Crop,data$Volume)
names(globtab)=c("ExportCountry","Crop","Volume")
globExpPer = globtab[,sum(Volume),by=ExportCountry]
names(globExpPer)=c("ExportCountry","Volume")
globExpPer$Perc=(globExpPer$Volume/totalImports)*100
barplot( globExpPer[globExpPer$Perc>5]$Perc,
        main = "Export Percentage",
        xlab = "Country",
        ylab = "%Export",
        names.arg = globExpPer[globExpPer$Perc>5]$ExportCountry,
        col = "darkred",
        horiz = FALSE,las=2)
```
Now we find rank of india. Since India is among the top exporters, we need not plot those with percentages less than 5 to find it's rank.
```{r}

globExpPer=globExpPer[order(globExpPer$Volume,decreasing=TRUE)]
barplot( globExpPer[globExpPer$Perc>5]$Perc,
        main = "Export Percentage",
        xlab = "Country",
        ylab = "%Export",
        names.arg = globExpPer[globExpPer$Perc>5]$ExportCountry,
        col = "darkred",
        horiz = FALSE,las=2)
```
Thus, we see India is 7th in the world.

## <a name="q3"></a> Question 3
<hr/>

Q. Find the first three crops having the highest exports from India. Plot their percentage export of the total exports from India.

A.
Below, we see that some crop names are not available in the dataset. So, We shall not be including that while finding the top crops exported from India.
```{r}
topcrop=globtab[globtab$ExportCountry=="India",]
top=topcrop[,sum(Volume), by=Crop]
names(top)=c("Crop","Volume")
top=top[order(top$Volume,decreasing = TRUE)]
totalImports=sum(top$Volume)
top
```
Soya bean seed takes the lead, Then soya beans and white sugar.
```{r}
topp=top[1:4,]
topp$perc=(topp$Volume/totalImports)*100
barplot( topp[topp$Crop!="",]$perc,
        main = "Export Percentage",
        xlab = "Crop",
        ylab = "%Export",
        names.arg = topp[topp$Crop!="",]$Crop,
        col = "darkred",
        horiz = FALSE,las=2)
```

## <a name="q4"></a> Question 4
<hr/>

Q. Plot the percentage of the class of different crops exported from India.

A.
```{r}
top$perc=(top$Volume/totalImports)*100
barplot( top[top$Crop!="",]$perc,
        main = "Export Percentage",
        xlab = "Crop",
        ylab = "%Export",
        names.arg = top[top$Crop!="",]$Crop,
        col = "darkred",
        horiz = FALSE,las=2)
```