---
title: "Lab8"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### S Shyam Sundaram
### 19BCE1560
### 27th September, 2021
### Dr. B. Radhika Selvamani
<br>

## Index
<hr/>
Click to go to the respective Question <br>
1. [Question 1](#q1) <br>
2. [Question 2](#q2) <br>
3. [Question 3](#q3) <br>

## <a name="q1"></a> Question 1
<hr/>

Q. Clean the given people death and birth data and read the values in to a dataframe.

A.
```{r}
(txt <- readLines("PeopleBirthDeathData.txt"))
T=grepl("%",txt)
data=txt[!T]

(records <- strsplit(data, split = ","))

formTable <- function(x){
  out <- character(4)
  # get names and gender
  i <- grep("[[:alpha:]]",x)
 
  out[1:2] <- x[i]
  #clean gender
  #out[2]<-ifelse(grepl("fem",out[2]),"female","male")
  
  # get birth date assuming all birth years to be earlier than 1890
  i <- which(as.numeric(x) < 1890)
  out[3] <- ifelse(length(i)>0, x[i], NA)
  # get death date assuming all death years to be after 1890
  i <- which(as.numeric(x) > 1890)
  out[4] <- ifelse(length(i)>0, x[i], NA)
  out
}

records <- lapply(records, formTable)

M <- matrix(unlist(records), nrow=length(records), byrow=TRUE)

#convert matrix to data frame
colnames(M) <- c("name","gender","birth","death")
daltons = as.data.frame(M, stringsAsFactors=FALSE)
daltons
```

## <a name="q2"></a> Question 2
<hr/>

Q. Convert the name of the person a character vector and the years to numerical vector. Calculate the age of the people and add it as a new column.

A. Name is already character. Just need to convert the years.
```{r}
typeof(unlist(daltons['name']))
daltons['birth']<-as.numeric(unlist(daltons['birth']))
daltons['death']<-as.numeric(unlist(daltons['death']))
typeof(unlist(daltons['death']))
typeof(unlist(daltons['birth']))
```
To calculate age:
```{r}
daltons<-transform(daltons,age=death-birth)
daltons
```

## <a name="q3"></a> Question 3
<hr/>

Q. Clean the gender data and convert it to a factor with values (male, female and NA)

A.

```{r}

for(i in 1:nrow(daltons))
{
        daltons[i,'gender']<-ifelse(grepl("fem",daltons[i,'gender']),"female","male")
}
daltons$gender
daltons
```