---
title: "Lab12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### S Shyam Sundaram
### 19BCE1560
### 20th November, 2021
### Dr. B. Radhika Selvamani
<br>

## Index
<hr/>
Click to go to the respective Question <br>
1. [Question 1](#q1) <br>
2. [Question 2](#q2) <br>

## <a name="q1"></a> Question 1
<hr/>

Q.Create a vector of all possible outcomes of throwing two dies.<br>

For eg.,<br>
1 ,1<br>
1,2<br>
1,3…..<br>
Create a table which shows the sum of the two dies and the  probability of getting all possible sums starting from 2 till 12.

<br><br>
A.
```{r}
m <- matrix(1/36, nrow=6, ncol=6)
su=rep(0,12)
for (i in 1:6)
{
  for(j in 1:6)
  {
    su[i+j]=m[i,j]+su[i+j]
  }
}
su[2:12]
```
The array above shows the probability of getting a sum from 2 to 12 with a apair of dice.<br><br>

#
## <a name="q2"></a> Question 2
<hr/>

Q. A lucky draw organized by Company A has the following rules<br>

a.	If three consecutive numbers are even the player loses Rs.1000<br>
b.	 If three consecutive numbers are odd the player gains Rs.1000<br>

For a given sequence of numbers, find out how much the player has lost or gained at the end.<br><br>
A.

```{r}
sequ<-c(7,1,5,3,2,4,8,3)
points<-0
iter<-length(sequ)-2
for (i in 1:iter)
{
  
  if (all((sequ[i:(i+2)]%%2)==0))
    {points=points-1000}
  else if (all((sequ[i:(i+2)]%%2)!=0))
  {
    points=points+1000
  }
}

points
```
<br>Total points are shown above. He gained 1000 points because:<br>
1. 7,1,5 gains 1000. Total=1000<br>
2. 1,5,3 gains 1000. Total=2000<br>
3. 5,3,2 doesn't change anything. similarly 3,2,4 doesn't affect anything.<br>
4. 2,4,8 loses 1000. Total=1000.<br>
5. 5,8,3 doesn't change anything.<br>
